Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network

### 2018-05-18 www-2018/source/paper.tex
Add old www source files.

\begin{abstract}
It is crucial for large-scale communication networks such as the internet
to be resilient against attacks\cite{sterbenz_resilience_2010}
such as censorship and surveillance,
which pose a threat to free expression and free association.
Self-organized networks such as the internet’s router network typically have
heavy-tailed degree distributions\cite{barabasi_scale-free_2009},
making them highly vulnerable to targeted attacks against central nodes
\cite{albert_error_2000}.
While cryptographic solutions exist,
they fail to address the underlying topological problem,
and remain vulnerable to
man-in-the-middle attacks \cite{nayak_different_2010}
and coercion \cite{grewal_caveat_2013}.
Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the
wraparound butterfly network topology,
as well as a highly attack-tolerant Structured Multipath Fault Tolerance (SMFT)
architecture which incorporates the butterfly CMR algorithm. We also identify a
previously unexplored relationship between network topology, trust transitivity,
and attack-tolerance, and provide a framework for further exploration of this
relationship. Our work is the first theoretical demonstration of a point-to-point
communication network architecture that can resist coercion and other
non-technical attacks, without requiring infinitely transitive trust.
To address cases where the network structure cannot be fully controlled,
we demonstrate how a snapshot of the internet’s router network can be partially
rewired for greater attack-tolerance.
More broadly, we hope that this work will serve as a starting point for the
development of additional topology-based attack-tolerant communication
architectures to guard against the dangers of censorship and surveillance.
\end{abstract}

@@

Our proposed architecture is differentiated from existing systems by several
properties (Table \ref{tab:compare}).
Decentralized architectures are more resistent to coercion
\cite{grewal_caveat_2013}
and man-in-the-middle attacks \cite{nayak_different_2010}.
Trust-based systems are more sustainable than proof-of-work.
Bounded-trust systems do not require the unrealistic assumption of infinite
trust transitivity.
Topological approaches address the root cause of vulnerability
in heavy-tail networks,
rather than relying on technology that can be side-stepped through coercion.
Point-to-point communication allows two individuals to exchange messages
without requiring large amounts of indefinite data storage on intermediate
nodes.

@@

Standard fault tolerance methods use redundancy to detect and correct
statistically independent faults.
In complex networks however, faults can be correlated when,
for example, two messages pass through the same faulty node.
For now, let us assume our sender (Alice) and receiver (Bob) are connected
by $\delta$ direct channels, with indpendent errors.
We will return to the question of constructing these channels in subsequent
sections.
For now, we concern ourselves with the question:
given that the network provides $\delta$ redundant channels between
Alice and Bob,
what is the probability that an adversary (Mal) causes an undetectable
error after causing faults in a fixed number of channels?

Let us first consider the scenario in which
Alice sends a message copy over each available channel.
We can also assume that each message includes the number of messages sent,
the full list of channels used, etc.,
making that information available to Bob.
When Bob receives the messages, there are several possibilities.
If some of the messages are missing
or if some of the messages disagree,
Bob knows that some of the messages were either blocked or altered,
and he has successfully tolerated the fault(s).
Bob can then take any of several actions:
1. request retransmission;
2. send receipts so Alice knows which paths have been compromised;
or 3. attempt error correction using majority voting.
If instead, Bob finds that all the messages are present and agree,
there are two possible cases.
The first case is that Mal has not compromised any of the messages,
and Bob has correctly accepted them, so no failure has occurred.
The second case is that Mal has compromised {\em all} of the messages,
so Bob has accepted an erroneous message and a failure has occurred.
In the present scenario,
whether a failure occurs depends only on whether Mal has the resources to
compromise all of the channels.
In a more realistic scenario,
both Alice and Mal have limited resources and are not able to use or
compromise all available channels.

@@

So far, we have assumed that Alice and Bob have access to some number
$\delta$ of channels with statistically indpendent faults.
However, in real communication architectures, direct links between all
pairs of individuals are not possible and messages must be routed through
a number of intermediate nodes.
In an adversarial setting,
the existence of intermediate nodes introduces two problems:
1. intermediate nodes may be compromised by the adversary and
2. faults on paths are no longer statistically independent:
two paths may pass through the same compromised node.
We show how to how to resolve these problems using a combination of network
structure and bounded trust transitivity.

@@

An alternative assumption might be that each hop away from Alice in
in the network reduces the probability that a node can resist compromise
by a multiplicatve constant.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, or less likely to take proactive security measures against that
adversary.
An even simpler version assumes that nodes up to some
fixed number of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define our model formally.

We define the {\em bounded trust model} on
an undirected graph $G = (V,E)$,
although the model can easily be extended to directed multigraphs.
Vertices representing commiunicating parties,
with edges representing mutually trusted communication links.
We define a {\em trust radius} $h$ such that nodes $v$ and
$w$ trust each other if their distance is less than $h$.
For a given node $v$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(v)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
and if compromised can entirely isolate $v$ from the rest of the network.

Now let $s \in V$ be an arbitrary sender
and $t \in V$ be an arbitrary receiver.
We assume the presence of an adversary who knows the
full structure of the network,
and who can compromise a fixed number of nodes,
gaining complete control of their behavior.
We also assume that the adversary is specifically targeting communicaiton
between $s$ and $t$ and
can compromise any node except for those trusted by $s$ or $t$.
Under these trust assumptions, adversarial faults can only occur
outside the trusted neighborhoods of $s$ and $t$:
$V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.
We now show how it is possible to communicate reliably,
even when all available paths go through the untrusted region.

@@

Our approach is to achieve fault tolerance through redundancy.
To do so, we must use only
{\em independent paths} \cite{reiter_resilient_1998},
which have no common points of failure.
Typically, it is assumed that in order to be independent,
paths must be internally vertex disjoint, i.e.,
have no nodes in common except the endpoints.
However, under the bounded trust model,
intersecting paths can still be independent if their
intersection contains only trusted nodes.
We define two paths with common endpoints
to be {\em $h$-internally vertex disjoint}
if all common vertices are less than distance $h$ from
one of the endpoints.
This condition holds if and only if two paths are indpendent
under the bounded trust model with radius $h$.

When trust radius $h$ is assumed,
the number of $h$-internally vertex disjoint paths between
two nodes $s$ and $t$ represents the number of
channels that can be constructed between them having
statistically indpendent faults.
We thus refer to this quantity as the 
{\em effective redundancy} $\delta_{s,t,h}$.
The effective redundancy can also be interpreted as the
max-flow/min-cut of a graph after each trusted neighborhood has been
collapsed into a single vertex.
The trust boundaries form a cut of the network and place an upper bound on the
min-cut:
\beq
\delta_{v,w,h} \leq \min\left( \mid B_h(s) \mid, \mid B_h(t) \mid \right).
\eeq
Equality holds when there are no bottlenecks within the untrusted region,
an indication that the network is decentralized.
The effective redundancy of the entire graph can be characterized by the minimum
over all vertex pairs:
\beq
\delta_h(G) \equiv \min_{s,t \in V} \delta_{s,t,h}.
\eeq
Thus, for any pair of nodes in the network, at least $\delta_h$ independent,
redundant paths can be constructed between them.
The more quickly $\delta_h$ grows with $h$,
the better a network is at leveraging trust transitivity to create redundancy.
Thus, the scaling of $\delta_h$ can be used to quantify a network's ability
to withstand targeted attacks,
even when the exact trust radius $h$ is unknown.

@@

Finding a maximal set of independent paths for an abitrary network is NP hard
\cite{reiter_resilient_1998},
posing a challenge for multipath fault tolerance.
We propose side-stepping this problem by using structured networks,
for which independent paths can be generated efficiently.
We call this approach {\em structured multipath fault tolerance} (SMFT),
and now proceed to show how it is implemented on the butterfly
network topology.

@@

In order to implement structured multipath fault tolerance,
we need a strucutred network topology with high effective redundancy.
In this paper, we apply SMFT to the butterfly network topology
\cite{kshemkalyani_distributed_2008}.
The structure of the butterfly network is highly constrained,
making it most suitable for applications where portions of the
network structure can be designed or dictated.
Examples of such networks include:
overlay networks \cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.
More flexible architectures may be possible,
but attack-tolerance will always require some level of influence over
network structure in order to limit single points of failure.
To address the case when the network cannot be fully controlled,
we show how partially rewiring a snapshot of the internet's router
network can greatly increase it's effective redundancy and
attack-tolerance properties.

@@

We choose the butterfly topology
\cite{kshemkalyani_distributed_2008}
because of several desirable properties (described below)
and because its structure allows for relatively straightforward
design and analysis of routing algorithms.
While several variations on the butterfly network exist,
we utilize the $m$-dimensional, directed wrap-around butterfly
(Figure \ref{fig:bf-route}),
denoted $\wbf(m)$:
\beq
\wbf(m) &=& (V, E_\downarrow \cup E_\rightarrow) \\
V &=& \mathbb{Z}_{m} \times \mathbb{Z}_2^m \\
E_\downarrow
&=&
\{((l,z),(l+1 \; (\text{mod } m),z) \} \\
E_\rightarrow
&=&
\{(l,z),(l+1 \; (\text{mod } m),
z \oplus 1_l \},
\eeq
where $\mathbb{Z}_m$ is the set of integers modulo $m$,
$\oplus$ represents componentwise addition modulo 2,
and $1_l$ is a vector with a 1 in index $l$ and 0 elsewhere.
Each node is associated with a level $l$ and an $m$-bit string $z$
known as {\em the place-within-level}.
There are two types of edges: down, and down-right
(shown in Figure \ref{fig:butterfly}).
Down edges ($E_\downarrow$) connect nodes sharing the same $z$ value
in a cycle of increasing level $l$.
Down-right edges ($E_\rightarrow$) also link to a node of level $l + 1$,
but one having the place-within-level equal to $z$ with the $l$th bit inverted.

@@

Our simulations show improved resistance to fragmentation and higher
effective redundancy when even a fraction of edges have been rewired to
match the butterfly topology.
While the original router network fragments when about 1\% of the nodes
have been removed (Figure \ref{fig:diameter}),
this number increases to 2\%
with only 10\% of the butterfly edges present.
With 90\% of the butterfly edges present
the network remains unfragmented beyond the failure of the 8\% most
central nodes.
The effective redundancy for varius values of trust transitivity $h$
are shown in Figure \ref{fig:mincut}.
The effective redundancy is calculated by collapsing nodes and edges within
$h$ hops of source and destination into single nodes and finding the mincut
between them,
averaging over 150 source-destination pairs.
For $h=0$, the rewired version has strictly higher redundancy.
For $h>0$,
the original network has higher redundancy when the number of failures is small,
while the rewired network has higher redundancy beyond a crossover point.
We interpret these results to suggest that even when a small number of
highly central nodes have been removed from a heavy-tailed network,
most nodes are still able to take advantage of the remaining hubs.
As larger hubs continue to be removed, the connectivity of the network
decreases until the crossover point,
at which point the rewired network offers higher effective redundancy.

@@

We now present a routing algorithm to construct $2^h$ independent paths
between two nodes in a butterfly network,
where $h$ is the trust radius under the partial trust model.
Informally, Alice sends each message to a distinct node on her
trust boundary, then to a distinct intermediate node in the untrusted region,
then to a distinct node on Bob's trust boundary, and finally to Bob.
The intermediate nodes are in a sense ``far'' from each other and ensure that
no two paths overlap in the untrusted region.
Each path can be parameterized by a single integer $s$, which identifies
the specific node on Alice's trust boundary
(or equivalentely the node on Bob's trust boundary, or the untrusted intermdiate).

@@

In its current form, our work has several limitations.
Most obviously, it requires complete control over the network structure.
However, we have shown that even partially control over network structure can
improve attack tolerance propeties.
Still a more flexible network structure is desirable.
There is also the question of how to construct such a network without a centeral
authority.
This limitation may not be as severe as it seems,
due to the nested structure of the butterfly network.
We conjecture that smaller independently-formed networks could be
merged into a single larger network without central coordination.

>>>>

\begin{abstract}
It is crucial for large-scale communication networks such as the internet
to be resilient against attacks\cite{sterbenz_resilience_2010}
such as censorship and surveillance,
which pose a threat to free expression and free association.
Self-organized networks such as the internet’s router network typically have
heavy-tailed degree distributions\cite{barabasi_scale-free_2009},
making them highly vulnerable to targeted attacks against central nodes
\cite{albert_error_2000}.
While cryptographic solutions exist,
they fail to address the underlying topological problem,
and remain vulnerable to
man-in-the-middle attacks \cite{nayak_different_2010}
and coercion \cite{grewal_caveat_2013}.
Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the
wraparound butterfly network topology,
as well as a highly attack-tolerant Structured Multipath Fault Tolerance (SMFT)
architecture which incorporates the butterfly CMR algorithm. We also identify a
previously unexplored relationship between network topology, trust transitivity,
and attack-tolerance, and provide a framework for further exploration of this
relationship. Our work is the first theoretical demonstration of a point-to-point
communication network architecture that can resist coercion and other
non-technical attacks, without requiring infinitely transitive trust.
To address cases where the network structure cannot be fully controlled,
we demonstrate how a snapshot of the internet’s router network can be partially
rewired for greater attack-tolerance.
%More broadly, we hope that this work will serve as a starting point for the
%development of additional topology-based attack-tolerant communication
%architectures to guard against the dangers of censorship and surveillance.
\end{abstract}

@@

Our proposed architecture is differentiated from existing systems by several
properties (Table \ref{tab:compare}).
Decentralized architectures are more resistant to coercion
\cite{grewal_caveat_2013}
and man-in-the-middle attacks \cite{nayak_different_2010}.
Trust-based systems are more sustainable than proof-of-work.
Bounded-trust systems do not require the unrealistic assumption of infinite
trust transitivity.
Topological approaches address the root cause of vulnerability
in heavy-tail networks,
rather than relying on technology that can be side-stepped through coercion.
Point-to-point communication allows two individuals to exchange messages
without requiring large amounts of indefinite data storage on intermediate
nodes.

@@

Standard fault tolerance methods use redundancy to detect and correct
statistically independent faults.
In complex networks however, faults can be correlated when,
for example, two messages pass through the same faulty node.
For now, let us assume our sender (Alice) and receiver (Bob) are connected
by $\delta$ direct channels, with independent errors.
We will return to the question of constructing these channels in subsequent
sections.
For now, we concern ourselves with the question:
given that the network provides $\delta$ redundant channels between
Alice and Bob,
what is the probability that an adversary (Mal) causes an undetectable
error after causing faults in a fixed number of channels?

Let us first consider the scenario in which
Alice sends a message copy over each available channel.
We can also assume that each message includes the number of messages sent,
the full list of channels used, etc.,
making that information available to Bob.
When Bob receives the messages, there are several possibilities.
If some of the messages are missing
or if some of the messages disagree,
Bob knows that some of the messages were either blocked or altered,
and he has successfully tolerated the fault(s).
Bob can then take any of several actions:
1. request re-transmission;
2. send receipts so Alice knows which paths have been compromised;
or 3. attempt error correction using majority voting.
If instead, Bob finds that all the messages are present and agree,
there are two possible cases.
The first case is that Mal has not compromised any of the messages,
and Bob has correctly accepted them, so no failure has occurred.
The second case is that Mal has compromised {\em all} of the messages,
so Bob has accepted an erroneous message and a failure has occurred.
In the present scenario,
whether a failure occurs depends only on whether Mal has the resources to
compromise all of the channels.
In a more realistic scenario,
both Alice and Mal have limited resources and are not able to use or
compromise all available channels.

@@

So far, we have assumed that Alice and Bob have access to some number
$\delta$ of channels with statistically independent faults.
However, in real communication architectures, direct links between all
pairs of individuals are not possible and messages must be routed through
a number of intermediate nodes.
In an adversarial setting,
the existence of intermediate nodes introduces two problems:
1. intermediate nodes may be compromised by the adversary and
2. faults on paths are no longer statistically independent:
two paths may pass through the same compromised node.
We show how to how to resolve these problems using a combination of network
structure and bounded trust transitivity.

@@

An alternative assumption might be that each hop away from Alice in
in the network reduces the probability that a node can resist compromise
by a multiplicative constant.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, or less likely to take proactive security measures against that
adversary.
An even simpler version assumes that nodes up to some
fixed number of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define our model formally.

We define the {\em bounded trust model} on
an undirected graph $G = (V,E)$,
although the model can easily be extended to directed multigraphs.
Vertices representing communicating parties,
with edges representing mutually trusted communication links.
We define a {\em trust radius} $h$ such that nodes $v$ and
$w$ trust each other if their distance is less than $h$.
For a given node $v$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(v)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
and if compromised can entirely isolate $v$ from the rest of the network.

Now let $s \in V$ be an arbitrary sender
and $t \in V$ be an arbitrary receiver.
We assume the presence of an adversary who knows the
full structure of the network,
and who can compromise a fixed number of nodes,
gaining complete control of their behavior.
We also assume that the adversary is specifically targeting communication
between $s$ and $t$ and
can compromise any node except for those trusted by $s$ or $t$.
Under these trust assumptions, adversarial faults can only occur
outside the trusted neighborhoods of $s$ and $t$:
$V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.
We now show how it is possible to communicate reliably,
even when all available paths go through the untrusted region.

@@

Our approach is to achieve fault tolerance through redundancy.
To do so, we must use only
{\em independent paths} \cite{reiter_resilient_1998},
which have no common points of failure.
Typically, it is assumed that in order to be independent,
paths must be internally vertex disjoint, i.e.,
have no nodes in common except the endpoints.
However, under the bounded trust model,
intersecting paths can still be independent if their
intersection contains only trusted nodes.
We define two paths with common endpoints
to be {\em $h$-internally vertex disjoint}
if all common vertices are less than distance $h$ from
one of the endpoints.
This condition holds if and only if two paths are independent
under the bounded trust model with radius $h$.

When trust radius $h$ is assumed,
the number of $h$-internally vertex disjoint paths between
two nodes $s$ and $t$ represents the number of
channels that can be constructed between them having
statistically independent faults.
We thus refer to this quantity as the 
{\em effective redundancy} $\delta_{s,t,h}$.
The effective redundancy can also be interpreted as the
max-flow/min-cut of a graph after each trusted neighborhood has been
collapsed into a single vertex.
The trust boundaries form a cut of the network and place an upper bound on the
min-cut:
\beq
\delta_{v,w,h} \leq \min\left( \mid B_h(s) \mid, \mid B_h(t) \mid \right).
\eeq
Equality holds when there are no bottlenecks within the untrusted region,
an indication that the network is decentralized.
The effective redundancy of the entire graph can be characterized by the minimum
over all vertex pairs:
\beq
\delta_h(G) \equiv \min_{s,t \in V} \delta_{s,t,h}.
\eeq
Thus, for any pair of nodes in the network, at least $\delta_h$ independent,
redundant paths can be constructed between them.
The more quickly $\delta_h$ grows with $h$,
the better a network is at leveraging trust transitivity to create redundancy.
Thus, the scaling of $\delta_h$ can be used to quantify a network's ability
to withstand targeted attacks,
even when the exact trust radius $h$ is unknown.

@@

Finding a maximal set of independent paths for an arbitrary network is NP hard
\cite{reiter_resilient_1998},
posing a challenge for multipath fault tolerance.
We propose side-stepping this problem by using structured networks,
for which independent paths can be generated efficiently.
We call this approach {\em structured multipath fault tolerance} (SMFT),
and now proceed to show how it is implemented on the butterfly
network topology.

@@

In order to implement structured multipath fault tolerance,
we need a structured network topology with high effective redundancy.
In this paper, we apply SMFT to the butterfly network topology
\cite{kshemkalyani_distributed_2008}.
The structure of the butterfly network is highly constrained,
making it most suitable for applications where portions of the
network structure can be designed or dictated.
Examples of such networks include:
overlay networks \cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.
More flexible architectures may be possible,
but attack-tolerance will always require some level of influence over
network structure in order to limit single points of failure.
To address the case when the network cannot be fully controlled,
we show how partially rewiring a snapshot of the internet's router
network can greatly increase it's effective redundancy and
attack-tolerance properties.

@@

We choose the butterfly topology
\cite{kshemkalyani_distributed_2008}
because of several desirable properties (described below)
and because its structure allows for relatively straightforward
design and analysis of routing algorithms.
While several variations on the butterfly network exist,
we utilize the $m$-dimensional, directed wrap-around butterfly
(Figure \ref{fig:bf-route}),
denoted $\wbf(m)$:
\beq
\wbf(m) &=& (V, E_\downarrow \cup E_\rightarrow) \\
V &=& \mathbb{Z}_{m} \times \mathbb{Z}_2^m \\
E_\downarrow
&=&
\{((l,z),(l+1 \; (\text{mod } m),z) \} \\
E_\rightarrow
&=&
\{(l,z),(l+1 \; (\text{mod } m),
z \oplus 1_l \},
\eeq
where $\mathbb{Z}_m$ is the set of integers modulo $m$,
$\oplus$ represents component-wise addition modulo 2,
and $1_l$ is a vector with a 1 in index $l$ and 0 elsewhere.
Each node is associated with a level $l$ and an $m$-bit string $z$
known as {\em the place-within-level}.
There are two types of edges: down, and down-right
(shown in Figure \ref{fig:butterfly}).
Down edges ($E_\downarrow$) connect nodes sharing the same $z$ value
in a cycle of increasing level $l$.
Down-right edges ($E_\rightarrow$) also link to a node of level $l + 1$,
but one having the place-within-level equal to $z$ with the $l$th bit inverted.

@@

Our simulations show improved resistance to fragmentation and higher
effective redundancy when even a fraction of edges have been rewired to
match the butterfly topology.
While the original router network fragments when about 1\% of the nodes
have been removed (Figure \ref{fig:diameter}),
this number increases to 2\%
with only 10\% of the butterfly edges present.
With 90\% of the butterfly edges present
the network remains unfragmented beyond the failure of the 8\% most
central nodes.
The effective redundancy for various values of trust transitivity $h$
are shown in Figure \ref{fig:mincut}.
The effective redundancy is calculated by collapsing nodes and edges within
$h$ hops of source and destination into single nodes and finding the min-cut
between them,
averaging over 150 source-destination pairs.
For $h=0$, the rewired version has strictly higher redundancy.
For $h>0$,
the original network has higher redundancy when the number of failures is small,
while the rewired network has higher redundancy beyond a crossover point.
We interpret these results to suggest that even when a small number of
highly central nodes have been removed from a heavy-tailed network,
most nodes are still able to take advantage of the remaining hubs.
As larger hubs continue to be removed, the connectivity of the network
decreases until the crossover point,
at which point the rewired network offers higher effective redundancy.

@@

We now present a routing algorithm to construct $2^h$ independent paths
between two nodes in a butterfly network,
where $h$ is the trust radius under the partial trust model.
Informally, Alice sends each message to a distinct node on her
trust boundary, then to a distinct intermediate node in the untrusted region,
then to a distinct node on Bob's trust boundary, and finally to Bob.
The intermediate nodes are in a sense ``far'' from each other and ensure that
no two paths overlap in the untrusted region.
Each path can be parameterized by a single integer $s$, which identifies
the specific node on Alice's trust boundary
(or equivalently the node on Bob's trust boundary, or the untrusted intermediate).

@@

In its current form, our work has several limitations.
Most obviously, it requires complete control over the network structure.
However, we have shown that even partially control over network structure can
improve attack tolerance properties.
Still a more flexible network structure is desirable.
There is also the question of how to construct such a network without a central
authority.
This limitation may not be as severe as it seems,
due to the nested structure of the butterfly network.
We conjecture that smaller independently-formed networks could be
merged into a single larger network without central coordination.
